An Implementation of the Active Contours without Edged model and the Logic Framework for Active contours on multi-channel images

### 2010-12-03 trunk/cs870/project/Report/Paper.tex
first 4 examples in chan vese

\subsection{Evaluation Criteria}
\label{sec:criteria}

In order to make sure we correctly implemented the models, we had several evaluation criteria. Table~\ref{tab:criteria} summarizes these criteria, and explains
the goals of each. For the rest of this section, we proceed by presenting our experimental results in the order of these criteria starting with the simplest
cases, and incrementally challenging the model.

\begin{table*}[h!t!]
\centering
\begin{tabular}{ c | c}
\textbf{Criteria} & \textbf{Goal} \\
\hline\hline
Detecting Boundaries & Ability to correctly detect object boundaries of simple objects\\
\hline
Curve Position & Ability to correctly detect object boundaries irrespective of the initial curve position\\
\hline
Detecting Holes & Ability to detect holes in objects, and not simply stop on outside boundary\\
\hline
Blurred Images & Ability to correctly (as much as possible) detect object boundaries in blurred images\\
\hline
Noisy Images & Ability to correctly (as much as possible) detect object boundaries in noisy images\\
\hline
Parameter Settings & Ability to respond correctly to the different parameter settings
\end{tabular}
\centering
\caption{Evaluation Criteria}
\label{tab:criteria}
\end{table*}

\subsection{Criteria 1: Successfully Detecting Boundaries}

>>>>

In order to make sure we correctly implemented the models, we had several evaluation criteria. Table~\ref{tab:criteria} summarizes these criteria, and explains
the goals of each. Some of these criteria apply for both models, while other apply to one or the other. For the rest of this section, we proceed by presenting
our experimental results for both models. For each model, we proceed in the order of these criteria starting with the simplest
cases, and incrementally challenging the model. Unless otherwise stated, all the segmentation was performed on a gray scale version of the original image.

\begin{table*}[h!t!]
\centering
\begin{tabular}{ c | c |c}
\textbf{Criteria} & \textbf{Goal} & \textbf{Applies to Model}\\
\hline\hline
Detecting Boundaries & Ability to correctly detect object boundaries of simple objects& Both Models\\
\hline
Curve Position & Ability to correctly detect object boundaries irrespective of the initial curve position & Both Models\\
\hline
Detecting Holes & Ability to detect holes in objects, and not simply stop on outside boundary & Both Models\\
\hline
Blurred Images & Ability to correctly (as much as possible) detect object boundaries in blurred images & Both Models\\
\hline
Noisy Images & Ability to correctly (as much as possible) detect object boundaries in noisy images & Both Models\\
\hline
Union Operator & Ability to correctly obtain the union of two or more images & Sandberg-Chan\\
\hline
Intersection Operator & Ability to correctly obtain the intersection of two or more images & Sandberg-Chan\\
\hline
Complement & Ability to correctly obtain the union or intersection of two or more images containing complements & Sandberg-Chan\\
\hline
Parameter Settings & Ability to respond correctly to the different parameter settings & Both Models\\
\end{tabular}
\centering
\caption{Evaluation Criteria}
\label{tab:criteria}
\end{table*}

\subsection{Chan-Vese Model Results}

\subsubsection*{Successful Detection of Boundaries}

Figure~\ref{fig:cv_eg1} shows that the implemented model can successfully detect object boundaries in a simple image. In this case, the evolving curve was
successfully able to detect the boundaries of both objects. Figure~\ref{fig:cv_eg2} shows a slightly more complicated example where the evolving contour
successfully detects the contour of the brain. Note that there is a tiny area to the bottom left of the brain that was also successfully detected.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg1.png}
\caption{Successful detection of object boundaries. Top: the evolving curve (in red) over time where the first image shows the initial contour.
Bottom: evolving segmentation over time until the objects are detected. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} + 75$, $\mu =
0.01$, no reinitialization, cpu = 2.9s, 7 iterations.}
\label{fig:cv_eg1}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg2.png}
\caption{Successful detection of object boundaries. Top: the evolving curve (in red) over time where the first image shows the initial contour.
Bottom: evolving segmentation over time until the object is detected. Size = 131 x 131, $\phi_{0}(x,y) = - \sqrt{(x - 65.6)^2 + (y - 65.5)^2)} + 32.8$, $\mu =
0.01$, no reinitialization, cpu = 1.95 s, took 7 iterations.}
\label{fig:cv_eg2}
\end{figure*}

\subsubsection*{Independence of Initial Curve Position}

To ensure that the position of the curve does not affect the final segmentation, we tested two other positions for the initial curve for the same brain image
used in Figure~\ref{fig:cv_eg2}. In Figure~\ref{fig:cv_eg2}, the initial contour was completely overlapping the object. Accordingly, we tried two other
positions. The first one is shown in Figure~\ref{fig:cv_eg3} where the initial contour only partially overlaps with the object. The second one is shown in
Figure~\ref{fig:cv_eg4} where the initial contour does not overlap the object in any part. Visually, the obtained segmentation was the same with a slightly
higher number of iterations and CPU time. In all three cases, the brain was correctly segmented. We compared the area segmented as the brain in each case to
make sure the same segmentation was obtained, and in each case, we got the same area of 0.5268. Note, however, that when part of the curve lies outside the
object, the definition of inside and outside changes since the curve becomes an open curve at one point. This should not make a difference as long as the
contour lies correctly at the boundaries of the object.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg3.png}
\caption{Initial curve position partially overlapping object. Top: the evolving curve (in red) over time where the first image shows the initial contour.
Bottom: evolving segmentation over time until the object is detected. Size = 131 x 131, $\phi_{0}(x,y) = - \sqrt{(x - 30)^2 + (y - 30)^2)} + 20$, $\mu =
0.01$, no reinitialization, cpu = 2.26 s, took 9 iterations.}
\label{fig:cv_eg3}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg4.png}
\caption{Initial curve position not overlapping any area of the object. Top: the evolving curve (in red) over time where the first image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 131 x 131, $\phi_{0}(x,y) = - \sqrt{(x - 120)^2 + (y - 120)^2)} + 10$,
$\mu =0.01$, no reinitialization, cpu = 2.01 s, took 9 iterations.}
\label{fig:cv_eg4}
\end{figure*}

\subsubsection*{Successful Detection of Holes}

In order to make sure the contour does not simply stop at the outside boundary of an object and ignore any details inside such as holes, we first tried a
simple donut example, and then tried two more complicated donut images.

\subsubsection*{Reasonable Performance with Blurred Images}

\subsubsection*{Reasonable Performance with Noisy Images}

\subsubsection*{Successful Response to Parameter Settings}

\subsubsection*{Other Tests}

flowers here

\subsection{Sandberg-Chan Model Results}

\subsubsection*{Successful Detection of Boundaries}

\subsubsection*{Independence of Initial Curve Position}

\subsubsection*{Successful Detection of Holes}

\subsubsection*{Reasonable Performance with Blurred Images}

\subsubsection*{Reasonable Performance with Noisy Images}

\subsubsection*{Union}

\subsubsection*{Intersection}

\subsubsection*{Complement}

\subsubsection*{Successful Response to Parameter Settings}

\subsubsection*{Other Tests}
